Inspiring Confidence and Easing Insecurity in the Pre-election period: The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections

### 2025-07-18 response_memo.qmd

---
title: "Response Memo"
author: Isaiah Espinoza
format: 
  hikmah-response-typst:
    keep-typ: true
    toc: false
    mainfont: STIX Two Text
    fontsize: 11pt
    bibliography: references.bib
    bibliographystyle: american-political-science-association.csl
---

I thank the Reviewers for taking time to provide their thoughtful and constructive comments to my research paper "*Effect of Recruiting Military Veterans on Confidence in 2024 US Elections*". I revised much of the initial manuscript by restructuring certain sections and added clarification where needed. The Reviewers' comments are cited or summarized in [red italicized text]{.memo-reviewer-inline}, and my responses are in black text. I include excerpts from my revised manuscript in [blue]{.memo-excerpt-inline}. Note that an ellipses ($...$) within an excerpt of the manuscript stands in for the main text.

@@

::: memo-reviewer
We understand that veterans are generally viewed positively, and that’s part of why this approach might work. However, in the data, we don’t see any direct measures of how respondents feel about veterans—there’s no pre-treatment baseline for that. I understand that the data might not allow for it, or that asking upfront could interfere with the treatment, but still---it leaves us wondering: what exactly is driving the results? Is it the idea of integrity, a feeling of safety or strength, or a sense of national service? We don’t really know. For this paper, it might be acceptable to say we’re building on prior work and that the cue is sufficient, but it would be helpful to acknowledge that gap more directly and discuss potential explanations.
:::

In response to [*Reviewer 1*]{.memo-reviewer-inline}'s comment above, I included the following text in the '**Limitations**' section,

::: memo-excerpt
## Limitations

The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections. No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment. Of course, inquiring into attitudes about veterans pre-treatment could prime respondents in a way that would contaminate the experiment. Moreover, responses to questions about veterans post-treatment might, indeed, be influenced by the treatment. This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results. That being said, attempting to understand and explain why veterans are viewed favorably in general goes beyond the scope of this study. This study relied on the literature showing that overwhelmingly positive perceptions of veterans persists among the public *writ large*. It is surely important for future work to focus on understanding why veterans are generally favored in order to posit a potential mechanism that transmits the effect of the veterans cue on confidence in elections.
:::

@@

::: memo-reviewer
You present H1 very clearly, which is great. However, later in the paper, there are additional expectations that seem like they could have been articulated as formal hypotheses too—perhaps H2, H3, or even sub-parts like H1a, H1b. While it’s not a major issue, clearer hypothesis structure would enhance readability and help clarify the paper’s logic as it progresses. Currently, it feels like a mix of formal and informal framing.
:::

Agreed. I revised and inserted the following hypotheses more formally, and also inserted text to make more explicit the reasoning behind the latter hypotheses. The text of the '**Hypotheses**' section is unchanged save for inclusion of the following text.

::: memo-excerpt
## Hypotheses

($...$)

> H~2~: Differences in confidence in elections in one's local area and confidence in elections in Maricopa County, AZ, will be smaller among those who are presented with an announcement that election officials are recruiting miilitary service veterans to work as election staff and volunteers compared to those presented with an announcement of recruitment efforts that do not mention military veterans.

($...$)

> H~3~: Among those who refute the legitimacy of the 2020 election results, those presented with an announcement that election officials are recruiting veteran service members for election jobs will be associated with greater levels of confidence in elections compared to those presented with an announcement of recruitment efforts that do not mention military veterans.

@@

There's scant research or evidence available to postulate a well-formed theory on the mechanism underlying the expected effects of veterans as a group on attitudes about institutions and processes, rather than on attitudes about persons or groups. That is to say, there's not much research on how the public feels, or what they think, about former members of the U.S. Armed Forces.
:::

## ***Reviewer 1***---***How generalizable are these results***

::: memo-reviewer
I appreciate your honesty about how the strongest effects appear in Maricopa County, and that we don’t observe the same impact when people consider their own local elections. That’s interesting in itself, but it raises questions—can this approach be effective in other areas? Would appointing veterans as officials in lower-salience places have any impact? Or is this cue only meaningful in scrutinized locations? You touch on this briefly, but expanding this section would add depth, particularly for readers contemplating its implications for future elections.
:::

I share [**Reviewer 1**]{.memo-reviewer-inline}'s concerns regarding whether results are generalizable. I do interpret results as somewhat limited, and accordingly aim to limit what can be justifiably said in that regard.

I acknowledge this limitation of the results with the excerpt below. Importantly, I also clarify that the source of this limitation does not arise from specifying the location in the vignette as Maricopa County, AZ, but rather results are limited because the survey items ask specifically about elections in Maricopa County, AZ.

::: memo-excerpt
The election setting specified in survey items might raise concerns about whether results are generalizable to other places or counties nationwide. That is, whether promoting the recruitment of veterans in *any* county nationwide would similarly increase confidence in elections, or whether effects of the veteran cue is limited to elections in Maricopa County, AZ or similar places.

Maricopa County was specified *in the vignettes* because of the increased scrutiny levied toward elections admin there after 2020. This doesn't mean, necessarily, that Maricopa County, AZ, would therefore be salient to respondents generally and for that reason, if at all. There's no problem in asking about confidence in elections nationwide and in local elections while still keeping Maricopa County as the setting in the vignettes; even though the setting is specified in the vignettes, the setting acts only as a stand-in for counties nationwide. Maricopa County is indicated as the setting in both the treatment and control vignettes, thus the only actual difference between conditions is constrained to the target group being recruited.

The problem arises because the subsequent survey questions ask specifically about elections in Maricopa County; I cannot attest to whether the effect of the veterans cue generalizes to confidence in elections in places other than Maricopa County. To be clear, this limitation arises because *subsequent survey questions ask respondents to consider elections in Maricopa County specifically*.
:::

@@

::: memo-excerpt
## Theory: Why Veterans

The theory tested in this study is this: when the public is informed that election officials are actively recruiting veteran military service members to work at election sites as staff or volunteers, their overall confidence in the fairness, accuracy, and integrity of the electoral process will improve. Said another way, insecurities over the integrity of elections administration and safety of voters lessen as the public learns that military service veterans are being sought out by election officials to staff or volunteer at election sites. The stimulating influence of veterans as a group in the abstract is expected to counteract distrust and insecurity pertaining to the institution of elections administration, as well as inspire greater trust in the same. This prompts an obvious question: why would information about efforts to recruit veterans to work as election staff and volunteers have any influence on confidence in elections?

Election officials don't focus on recruiting people of a particular demographic, status, class, or prestige in order to shore up public trust in elections, and they don't discriminate recruitment efforts based on who the public thinks is best suited to secure elections from fraud. Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work. Especially since staffing has been an issue since at least the 1990s [@maidenberg1996; @ferrer2024]. In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a]. There's no special reason to target veterans for recruitment above other groups. Indeed, there's no reason to discriminate recruitment efforts at all if the point is purely to fill staffing vacancies.

There was a sudden push to target veterans for recruitment efforts ($...$)

One can speculate that ($...$)

@@

The kind of *trust in elections* I refer to concerns the expectations drawn up from one's judgement about the functioning of the electoral process---the extent to which one is assured in the belief that the electoral process will be fairly and accurately administered. I follow the notion of public trust in elections explicated by @stewart2022,

> "Public trust in U.S. election institutions comes down to whether voting machines accurately record votes, voter registration systems accurately record those eligible to vote, geographic information systems accurately assign voters to voting districts, election-night reporting systems accurately aggregate and communicate election results to officials and the public, and postelection audit and canvassing procedures proceed impartially and in accordance with the law." [-@stewart2022, 236]

That being said, I also account for expectations of electoral fraud, which I refer to as *distrust* in elections distinguished from trust. Distrust in this sense is also a belief, an expectation, about the anticipated functioning of the process. Note, however, that the prefix *dis-* in distrust implies "apart", "lack of, not" or "opposite". Conventionally, distrust is defined simply as the absence of trust, thus denoting a simple inverse and mutually exclusive relationship. However, as it concerns the psychology of an individual, *a lack of trust doesn't necessarily imply opposite expectations or opposing beliefs*. In particular, a lack of trust that votes will be accurately recorded, etc., doesn't necessarily imply inversely proportional expectations that electoral fraud will occur. In other words, although the relationship between trust and distrust is inverse, this relationship is not mutually exclusive.

As such, trust and distrust represent opposing degrees of confidence along the same spectrum. However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling relatively confident in both respects. Accordingly, *equivalent degrees of trust and distrust cancel out*, rendering one relatively more *insecure* about their expectations of the future despite the fact that they may report feeling confident in either direction respectively. When trust and distrust are considered reflective of one's confidence about future expectations, then both can be placed along the same spectrum. Therefore, a lack of confidence denotes insecurity.

With respect to the administration of U.S. elections, the confident voter expects that votes will be counted as voters intend, election staff will competently administer elections, election technology will be secure from nefarious tampering, and that the process will be fair for all involved.
:::

@@

Among the sample, $34.11\%$ ($n = 439$) said they had an immediately family member who was currently serving or had previously served in the U.S. military; $64.72\%$ ($n = 833$) didn't have a family member who served. Approximately $8.24\%$ ($n = 106$) of the sample were veterans, while $1.17\%$ ($n = 15$) reported to be actively serving.
:::

## ***Reviewer 2***---***Findings***

::: memo-reviewer
The author identifies heterogeneous effects by election level (local vs. national), which is a fascinating and potentially important finding. But what does this mean substantively? Do voters view the stakes of “local” and “national” elections differently with respect to legitimacy? Do they associate veterans with one level more than another?
:::

It is important to emphasize that results are limited to comparison of heterogeneous effects at between confidence in Maricopa County, AZ elections versus and local area elections, and should not be mistaken as demonstrating heterogeneous effects on confidence in elections at the national versus local level.

@@

::: memo-excerpt
It is difficult to compare magnitude of effect with other studies given that the item number, item wording, measurement, and computation of confidence in elections is unique across most individual studies to include this one. For instance, @gaudette2025 doesn't compose multiple items into a single composite measure, but subtracts pre-treatment values from post-treatment values for single-item measures with Likert-style response options. Whereas @clayton2023 develops a scale referred to as "Trust in American electoral process" by taking the mean from three items. The item wording of that scale is markedly similar to the items used to compose the trust scale of this study, but the range of response options differs considerably. Thus, while most studies examining public confidence in elections often include the core question "How confidence are you that your vote \[will be/was\] counted as you intended in the most recent election?", the different ways that researchers measure and compute variable scores on the outcome are most often, and unfortunately, sample dependent. The study of public confidence in elections is in desperate need of a standard method of measurement, or even a screened and validated item bank, and this study may be seen as a baby step to that end.

That being said, this study generally emulates treatment effects of comparable studies in the literature. @gaudette2025 found positive effects of official messaging from election officials on various items measuring trust in elections and expectations of electoral fraud. Similarly, @clayton2023, confined to a sample of Republican participants, found positive influence on perceptions of 2020 election legitimacy and trust in the American electoral process from official messaging by Republican politicians reaffirming the 2020 election results.
:::

::: memo-reviewer
I also encourage more discussion of null results. Even where effects are weak or absent, that tells us something important—especially if veteran cues only resonate among certain audiences or in certain electoral contexts.
:::

### 2025-07-18 docs/_tex/index.tex
modified revisions

Trust is, after all, merely \emph{belief} held in the face of
uncertainty. Trust is reliance on the veracity of belief in the face of
uncertainty. Said another way, trust is \emph{assured belief} dependent
on its supposed veracity; a state of certainty with respect to some
belief or judgement. It is ``\emph{assured}'' because it is one's belief
that relies on something rather than nothing. Hence quantitative methods
of the sciences are replete with things such as \emph{confidence}
intervals around our estimates. Therefore, I understand trust to refer
to the state or quality of certainty around one's beliefs or
expectations; the extent to which one is assured of their expectations
regarding what is or what will be the case.

@@

A person who is certain that electoral fraud will occur clearly lacks
trust in elections; an expectation that electoral fraud will occur
necessarily implies a lack of trust in elections regardless of positive
expressions of trust. However, the reverse isn't also true; expressing a
lack of trust in elections \emph{doesn't necessarily imply} an
expectation that electoral fraud will occur. Rather, a lack of trust
implies an absence of assurance in the belief that the process will be
conducted fairly and accurately---a lacking quality of certainty around
said belief. An absence of such assurance denotes a state of
\emph{insecurity}. Other sources of uncertainty may challenge a person's
confidence regarding the integrity of elections independent from
anything that would lead them to believe electoral fraud will occur or
has occurred. However my use of distrust refers to the assured belief
that the outcome will be invalid---that outcomes will be independent of
the process as prescribed, thus rendering outcomes as arbitrary.
Specifically, distrust implies assurance in the belief that electoral
fraud will occur.

As such, trust and distrust represent opposing degrees of confidence
along the same spectrum. However, despite the inherent contrast, one can
hold both positive degrees of trust and distrust, feeling relatively
confident in both respects. Accordingly, \emph{equivalent degrees of
trust and distrust cancel out}, rendering one relatively more insecure
about their expectations of the future despite the fact that they may
report feeling confident in either direction respectively. When trust
and distrust are considered reflective of one's confidence about future
expectations, then both can be placed along the same spectrum.
Therefore, a lack of confidence denotes insecurity.

This means that a person's baseline level of confidence in elections
must take into account their present degree of distrust---i.e., their
expectations of electoral fraud. Something may cause a person to have
greater expectations that election fraud will occur, which in turn will
always lower their trust in elections. In contrast, a person's trust in
the integrity of the electoral process is reduced by the extent to which
they expect that electoral fraud will occur.

Thus, it follows that a person distrusts the integrity of the electoral
process to the extent that they are to some extent certain that
electoral fraud will occur or has occurred. They are, perhaps, poised to
discount election results as invalid or illegitimate in advance. Either
way, both trust and distrust refer to some positive degree of confidence
(i.e., assurance) regarding one's expectations. They are distinguished
by reference to either the normative idea about what \emph{should} come
about, or what is \emph{supposed} to come about given the logical
structure and integrity of the process. If the structure and integrity
of some process is coherent and secure, respectively, then the outcome
that follows will be valid. Should the integrity of that process be
damaged or opaque, then the process becomes vulnerable and validity of
the results are open to challenge. With respect to the administration of
U.S. elections, the confident voter expects that votes will be counted
as voters intend, election staff will competently administer elections,
election technology will be secure from nefarious tampering, and that
the process will be fair for all involved.

@@

In their research examining whether groups differed in attitudes about
veterans, Kleykamp, Hipes, and MacLean
(\citeproc{ref-kleykamp2018}{2018}) could only speculate as to why
levels of support were lowest among Hispanic and Black respondents.
Their study was distinctive in that it stands as a rare case in which
public attitudes about veteran military members was the specific focus
of inquiry as opposed to studies that examine public opinion about the
military in general. Other research has found that attitudes about the
U.S. military generally---though not about active or veteran military
service members in particular---differs by race and ethnicity to varying
extents, but also could not supply reason for one groups' sentiment over
another\footnote{Note, however, that the sample examined by Nichols
  (\citeproc{ref-nichols2015}{2015}) was constrained to Texas residents,
  and the military-related issues concerned, among other things, favor
  for reinstatement of a military draft, support for allowing
  undocumented immigrants who live in the U.S. to serve in the U.S.
  Armed Forces, and whether undocumented immigrants should be granted
  U.S. citizenship as a result of military service. Although the authors
  found high overall support for the military as an institution, the
  other military-related attitudes of interest diverge far from public
  opinion about veterans. As such, differential effects found among
  different racial or ethnic groups likely have little to do with
  attitudes about former or active military service members.}
(\citeproc{ref-nichols2015}{Nichols 2015}).

Other studies have drawn out disparities in public attitudes about
veterans but in ways that are mostly indirect, i.e., without assessing
public regard for veterans directly. One overarching issue is that
there's limited research that differentiates public regard for veteran
and active military service members from the U.S. military as an
institution in general. Some studies assess public regard for veterans
indirectly by examining whether, and to what extent, endorsement of
certain policies differentiate by whether such policies benefit veterans
or the public generally. In one such study by Tsai et al.
(\citeproc{ref-tsai2021}{2021}), Republican partisanship was shown to be
the most consistent factor associated with more favorable attitudes
(e.g., compassion) toward homelessness and PTSD among the veteran
population, but not among the general adult population. Additionally,
Republican partisans tended to show greater support for federal funding
for homelessness and PTSD research when the reference population was
military veterans. That study, however, suggests that the effect of the
veteran status cue is sensitive to the topic in question.

Perhaps unsurprisingly, military veterans appear to be uniquely
deserving in the eyes of Republican partisans
(\citeproc{ref-mcdermott2015}{McDermott and Panagopoulos 2015};
\citeproc{ref-richardson2022}{Richardson 2022};
\citeproc{ref-tsai2021}{Tsai et al. 2021}). As such, military veteran
status may qualify favorable attitudes among Republican partisans
whereas their regard for other non-veteran groups might otherwise
express contempt or indifference. This further indicates a need for
research to determine an underlying mechanism explaining why, and for
whom, veterans incur special favor.

@@

The bluntness of the experimental stimulus and survey items don't allow
us to establish exactly what it is about military veterans in particular
that cues stronger confidence in elections. No survey items assessed
public attitudes about military veterans specifically, pre- nor
post-treatment. This unfortunately leaves no room for me to postulate
and examine any potential mechanisms underlying results.

It should be noted that these results are limited to one's expectations
in anticipation of election night. Whether the increase in confidence is
sustained post-election night cannot be inferred from these results.
Moreover, It is yet unclear whether actually encountering and
interacting with veterans working as staff or volunteers at election
sites does much to improve voter confidence after election night
compared to anyone else. It may be the case that assumptions that
veterans are filling spots as election workers and volunteers simply
primes positive expectations as one heads into an election site,
potentially improving voters perceptions of their own experience on the
way out. Further research would be needed to test such an idea.

The setting of the vignette and specified in survey items might raise
additional concerns on whether results are generalizable. Naming a
specific county in the vignette adds in a potentially influential factor
unaccounted for in the survey; some people may have attitudes about the
county in question, others won't, while others may be muffed to consider
a random county in the U.S. they know nothing about. Naming a real and
somewhat salient county potentially undermines confidence that the
treatment effects are solely attributable to veterans to an unknown
degree. Simply put, there may be something special about Maricopa
County, AZ in particular that generalizes across attitudes of trust or
distrust in elections.

Arguably, however, Maricopa County is indicated as the setting in both
the treatment and control vignettes, thus the only actual difference
between conditions is constrained to the target group being recruited.
Future research may employ vignettes naming a fictional U.S. county to
hopefully eliminate the setting as a concern. Alternatively additional
survey items that ask directly about one's knowledge or sentiment about
the county in question could inform researchers on whether the named
county imposes any undue influence at all, or whether the setting is
associated with other factors such as partisanship.

@@

Note also that the measurement items of the components trust and
distrust, and the method of computing scores for the dependent variable,
confidence in elections, are unique to this study but falls under the
methodological framework of Classical Test Theory (CTT). Although survey
measurement items were either directly drawn from or inspired by similar
survey items found in various other surveys (e.g., SPAE, Pew), the
question wording, response choices, coding, and computation of sum
scores of the dependent variable are specific, thus rendering
measurement of the hypothetical constructs of interest (i.e., trust,
distrust) less comparable across similar studies that profess
measurement of similar constructs (\citeproc{ref-widaman2024}{Widaman
and Revelle 2024}). Namely, trust, distrust, or confidence in elections
as defined and measured here.

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{1}
\bibitem[\citeproctext]{ref-abbate2020a}
Abbate, Andrea. 2020. {``39 {Ways Election Offices} Are {Responding} to
{COVID-19}.''} \emph{Center for Tech and Civic Life}.

@@

\bibitem[\citeproctext]{ref-baldor2025c}
Baldor, Lolita. 2025a. {``Military Commanders Will Be Told to Send
Transgender Troops to Medical Checks to Oust Them.''} \emph{AP News}.

\bibitem[\citeproctext]{ref-baldor2025a}
Baldor, Lolita. 2025b. {``Military Parade to Celebrate the {Army}'s
250th Anniversary Will Be Held on {Trump}'s Birthday.''} \emph{AP News}.

\bibitem[\citeproctext]{ref-baldor2025b}
Baldor, Lolita. 2025c. {``Pentagon Directs Military to Pull Library
Books That Address Diversity, Anti-Racism, Gender Issues.''} \emph{AP
News}.

\bibitem[\citeproctext]{ref-baldor2020}
Baldor, Lolita C. 2020. {``Military Wary That Shakeup Could Upend Its
Apolitical Nature.''} \emph{AP News}.

\bibitem[\citeproctext]{ref-baldor2025}
Baldor, Lolita C. 2025. {``Hegseth Orders the Name of Gay Rights
Activist {Harvey Milk} Scrubbed from {Navy} Ship.''} \emph{AP News}.

@@

\bibitem[\citeproctext]{ref-brennancenterforjustice2024}
Brennan Center for Justice. 2024. \emph{Local {Election Officials
Survey} --- {May} 2024 {\textbar} {Brennan Center} for {Justice}}.
Brennan Center Research Department.

@@

\bibitem[\citeproctext]{ref-carter2024}
Carter, Luke, Ashlan Gruwell, J Quin Monson, and Kelly D Patterson.
2024. {``From {Confidence} to {Convenience}: {Changes} in {Voting
Systems}, {Donald Trump}, and {Voter Confidence}.''} \emph{Public
Opinion Quarterly} 88(SI): 516--35.
doi:\href{https://doi.org/10.1093/poq/nfae034}{10.1093/poq/nfae034}.

@@

\bibitem[\citeproctext]{ref-coll2024a}
Coll, Joseph A, and Christopher J Clark. 2024. {``A {Racial Model} of
{Electoral Reform}: {The Relationship} Between {Restrictive Voting
Policies} and {Voter Confidence} for {Black} and {White Voters}.''}
\emph{Public Opinion Quarterly} 88(SI): 561--84.
doi:\href{https://doi.org/10.1093/poq/nfae032}{10.1093/poq/nfae032}.

\bibitem[\citeproctext]{ref-conde2020}
Conde, Ximena. 2020. {``Philly Area Counties Say Efforts to Recruit Poll
Workers for {Election Day} Are Paying Off.''} \emph{WHYY NPR}.

@@

\bibitem[\citeproctext]{ref-cooter2013}
Cooter, Amy. 2013. {``Americanness, {Masculinity}, and {Whiteness}: {How
Michigan Militia Men Navigate Evolving Social Norms}.''} Thesis.

\bibitem[\citeproctext]{ref-cooter2024}
Cooter, Amy. 2024. {``Veterans and {Extremism}: {From Militias} to
{January} 6th and {Real Patriots} {\textbar} {Middlebury Institute} of
{International Studies} at {Monterey}.''}

@@

\bibitem[\citeproctext]{ref-doubek2024}
Doubek, James. 2024. {``States and Cities Beef up Security to Prepare
for Potential Election-Related Violence.''} \emph{NPR}.

\bibitem[\citeproctext]{ref-dunn2018}
Dunn, Amina. 2018. {``Elections in {America}: {Concerns Over Security},
{Divisions Over Expanding Access} to {Voting}.''} \emph{Pew Research
Center}.

\bibitem[\citeproctext]{ref-edlin2024}
Edlin, Ruby, and Lawrence Norden. 2024. {``Poll of {Election Officials
Finds Concerns About Safety}, {Political Interference} {\textbar}
{Brennan Center} for {Justice}.''} \emph{Brennan Center For Justice}.

\bibitem[\citeproctext]{ref-ferrer2024}
Ferrer, Joshua, Daniel M Thompson, and Rachel Orey. 2024. \emph{Election
{Official Turnover Rates} from 2000--2024}. Bipartisan Policy Center.

@@

\bibitem[\citeproctext]{ref-garamone2016a}
Garamone, Jim. 2016a. {``Active-{Duty Personnel Must Remain Apolitical},
{Nonpartisan}, {Dunford Says}.''} \emph{DOD News {\textbar} U.S.
Department of Defense}.

\bibitem[\citeproctext]{ref-garamone2016}
Garamone, Jim. 2016b. {``{DOD} Civilians, Service Members Must Remain
Non-Partisan, Apolitical.''} \emph{DOD News {\textbar} U.S. Department
of Defense}.

@@

\bibitem[\citeproctext]{ref-giles2021}
Giles, Ben. 2021. {``Arizona {Recount Of} 2020 {Election Ballots Found
No Proof Of Corruption}.''} \emph{NPR}.

@@

\bibitem[\citeproctext]{ref-herndon2020}
Herndon, Astead W. 2020. {``{LeBron James} and a {Multimillion-Dollar
Push} for {More Poll Workers}.''} \emph{The New York Times}.

@@

\bibitem[\citeproctext]{ref-kleykamp2023}
Kleykamp, Meredith, Daniel Schwam, and Gilad Wenig. 2023. \emph{What
{Americans Think About Veterans} and {Military Service}: {Findings} from
a {Nationally Representative Survey}}. RAND Corporation.

>>>>

Trust is, after all, merely \emph{belief} held in the face of
uncertainty. Trust is reliance on the veracity of belief in the face of
uncertainty. Said another way, trust is \emph{assured belief} dependent
on its supposed veracity; a state of certainty with respect to some
belief or judgement. It is ``assured'' because it is one's belief that
relies on something rather than nothing. Hence quantitative methods of
the sciences are replete with things such as \emph{confidence} intervals
around our estimates. Therefore, I understand trust to refer to the
state or quality of certainty around one's beliefs or expectations; the
extent to which one is assured of their expectations regarding what is
or what will be the case.

@@

As such, trust and distrust represent opposing degrees of confidence
along the same spectrum. However, despite the inherent contrast, one can
hold both positive degrees of trust and distrust, feeling relatively
confident in both respects. Accordingly, \emph{equivalent degrees of
trust and distrust cancel out}, rendering one relatively more
\emph{insecure} about their expectations of the future despite the fact
that they may report feeling confident in either direction respectively.
When trust and distrust are considered reflective of one's confidence
about future expectations, then both can be placed along the same
spectrum. Therefore, a lack of confidence denotes insecurity.

With respect to the administration of U.S. elections, the confident
voter expects that votes will be counted as voters intend, election
staff will competently administer elections, election technology will be
secure from nefarious tampering, and that the process will be fair for
all involved.

@@

@@

The bluntness of the experimental stimulus and survey items don't allow
us to establish exactly what it is about military veterans in particular
that cues stronger confidence in elections. No survey items assessed
public attitudes about military veterans specifically, pre- nor
post-treatment. Of course, inquiring into attitudes about veterans
pre-treatment could prime respondents in a way that would contaminate
the experiment. Moreover, responses to questions about veterans
post-treatment might, indeed, be influenced by the treatment. This
unfortunately leaves no room for me to postulate and examine any
potential mechanisms underlying results. That being said, attempting to
understand and explain why veterans are viewed favorably in general goes
beyond the scope of this study. This study relied on the literature
showing that overwhelmingly positive perceptions of veterans persists
among the public \emph{writ large}. It is surely important for future
work to focus on understanding why veterans are generally favored in
order to posit a potential mechanism that transmits the effect of the
veterans cue on confidence in elections.

The election setting specified in survey items might raise concerns
about whether results are generalizable to other places or counties
nationwide. That is, whether promoting the recruitment of veterans in
\emph{any} county nationwide would similarly increase confidence in
elections, or whether effects of the veteran cue is limited to elections
in Maricopa County, AZ or similar places.

Maricopa County was specified \emph{in the vignettes} because of the
increased scrutiny levied toward elections admin there after 2020. This
doesn't mean, necessarily, that Maricopa County, AZ, would therefore be
salient to respondents generally and for that reason, if at all. There's
no problem in asking about confidence in elections nationwide and in
local elections while still keeping Maricopa County as the setting in
the vignettes; even though the setting is specified in the vignettes,
the setting acts only as a stand-in for counties nationwide. Maricopa
County is indicated as the setting in both the treatment and control
vignettes, thus the only actual difference between conditions is
constrained to the target group being recruited.

The problem arises because the subsequent survey questions ask
specifically about elections in Maricopa County; I cannot attest to
whether the effect of the veterans cue generalizes to confidence in
elections in places other than Maricopa County. To be clear, this
limitation arises because \emph{subsequent survey questions ask
respondents to consider elections in Maricopa County specifically}.

@@

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{1}
\bibitem[\citeproctext]{ref-abbate2020a}
Abbate, Andrea. 2020. {``39 {Ways Election Offices} Are {Responding} to
{COVID-19}.''}
\url{https://www.techandciviclife.org/covid-19-responses/}.

@@

\bibitem[\citeproctext]{ref-baldor2025c}
Baldor, Lolita. 2025a. {``Military Commanders Will Be Told to Send
Transgender Troops to Medical Checks to Oust Them.''}
\url{https://apnews.com/article/transgender-ban-military-discharge-troops-0218f0b6fec595c420bd0ac072d87335}.

\bibitem[\citeproctext]{ref-baldor2025a}
Baldor, Lolita. 2025b. {``Military Parade to Celebrate the {Army}'s
250th Anniversary Will Be Held on {Trump}'s Birthday.''}
\url{https://apnews.com/article/trump-army-military-parade-birthday-2f5cd12c8ccd4efddc29bfa3cf8f2705}.

\bibitem[\citeproctext]{ref-baldor2025b}
Baldor, Lolita. 2025c. {``Pentagon Directs Military to Pull Library
Books That Address Diversity, Anti-Racism, Gender Issues.''}
\url{https://apnews.com/article/pentagon-hegseth-dei-library-books-770364ab99591402ddffe8758432ff26}.

\bibitem[\citeproctext]{ref-baldor2020}
Baldor, Lolita C. 2020. {``Military Wary That Shakeup Could Upend Its
Apolitical Nature.''}
\url{https://apnews.com/article/military-wary-shakeup-upend-apolitical-89eccf0aef7cf7b99208b3bfd0453a43}.

\bibitem[\citeproctext]{ref-baldor2025}
Baldor, Lolita C. 2025. {``Hegseth Orders the Name of Gay Rights
Activist {Harvey Milk} Scrubbed from {Navy} Ship.''}
\url{https://apnews.com/article/harvey-milk-navy-ship-renamed-pride-month-d6cda5df15ee5bc066092d54c591c6f2}.

@@

\bibitem[\citeproctext]{ref-brennancenterforjustice2024}
Brennan Center for Justice. 2024. \emph{Local {Election Officials
Survey} --- {May} 2024 \textbar{} {Brennan Center} for {Justice}}.
Brennan Center Research Department.
\url{https://www.brennancenter.org/our-work/research-reports/local-election-officials-survey-may-2024}
(November 5, 2024).

@@

\bibitem[\citeproctext]{ref-carter2024}
Carter, Luke, Ashlan Gruwell, J Quin Monson, and Kelly D Patterson.
2024. {``From {Confidence} to {Convenience}: {Changes} in {Voting
Systems}, {Donald Trump}, and {Voter Confidence}.''} \emph{Public
Opinion Quarterly} 88: 516--35.
doi:\href{https://doi.org/10.1093/poq/nfae034}{10.1093/poq/nfae034}.

@@

\bibitem[\citeproctext]{ref-coll2024a}
Coll, Joseph A, and Christopher J Clark. 2024. {``A {Racial Model} of
{Electoral Reform}: {The Relationship} Between {Restrictive Voting
Policies} and {Voter Confidence} for {Black} and {White Voters}.''}
\emph{Public Opinion Quarterly} 88: 561--84.
doi:\href{https://doi.org/10.1093/poq/nfae032}{10.1093/poq/nfae032}.

\bibitem[\citeproctext]{ref-conde2020}
Conde, Ximena. 2020. {``Philly Area Counties Say Efforts to Recruit Poll
Workers for {Election Day} Are Paying Off.''} \emph{WHYY NPR}.
\url{https://whyy.org/articles/philly-area-counties-say-efforts-to-recruit-poll-workers-for-election-day-are-paying-off/}.

@@

\bibitem[\citeproctext]{ref-cooter2013}
Cooter, Amy. 2013. {``Americanness, {Masculinity}, and {Whiteness}: {How
Michigan Militia Men Navigate Evolving Social Norms}.''} Thesis.
\url{http://deepblue.lib.umich.edu/handle/2027.42/98077}.

\bibitem[\citeproctext]{ref-cooter2024}
Cooter, Amy. 2024. {``Veterans and {Extremism}: {From Militias} to
{January} 6th and {Real Patriots} \textbar{} {Middlebury Institute} of
{International Studies} at {Monterey}.''}
\url{https://www.middlebury.edu/institute/academics/centers-initiatives/ctec/ctec-publications/veterans-and-extremism-militias-january-6th}.

@@

\bibitem[\citeproctext]{ref-doubek2024}
Doubek, James. 2024. {``States and Cities Beef up Security to Prepare
for Potential Election-Related Violence.''} \emph{NPR: 2024 Election}.
\url{https://www.npr.org/2024/11/04/nx-s1-5178083/national-guard-police-election-security}
(November 5, 2024).

\bibitem[\citeproctext]{ref-dunn2018}
Dunn, Amina. 2018. {``Elections in {America}: {Concerns Over Security},
{Divisions Over Expanding Access} to {Voting}.''}
\url{https://www.pewresearch.org/politics/2018/10/29/elections-in-america-concerns-over-security-divisions-over-expanding-access-to-voting/}.

\bibitem[\citeproctext]{ref-edlin2024}
Edlin, Ruby, and Lawrence Norden. 2024. {``Poll of {Election Officials
Finds Concerns About Safety}, {Political Interference} \textbar{}
{Brennan Center} for {Justice}.''}
\url{https://www.brennancenter.org/our-work/analysis-opinion/poll-election-officials-finds-concerns-about-safety-political}.

\bibitem[\citeproctext]{ref-ferrer2024}
Ferrer, Joshua, Daniel M Thompson, and Rachel Orey. 2024. \emph{Election
{Official Turnover Rates} from 2000--2024}. Bipartisan Policy Center.
\url{https://bipartisanpolicy.org/download/?file=/wp-content/uploads/2024/04/WEB_BPC_Elections_Admin_Turnover_R01.pdf}.

@@

\bibitem[\citeproctext]{ref-garamone2016a}
Garamone, Jim. 2016a. {``Active-{Duty Personnel Must Remain Apolitical},
{Nonpartisan}, {Dunford Says}.''}
\url{https://www.defense.gov/News/News-Stories/Article/Article/881624/active-duty-personnel-must-remain-apolitical-nonpartisan-dunford-says}.

\bibitem[\citeproctext]{ref-garamone2016}
Garamone, Jim. 2016b. {``{DOD} Civilians, Service Members Must Remain
Non-Partisan, Apolitical.''}
\url{https://www.defense.gov/News/Releases/Release/Article/975910/dod-civilians-service-members-must-remain-non-partisan-apolitical}.

@@

\bibitem[\citeproctext]{ref-giles2021}
Giles, Ben. 2021. {``Arizona {Recount Of} 2020 {Election Ballots Found
No Proof Of Corruption}.''} \emph{NPR: 2024 Election}.
\url{https://www.npr.org/2021/09/25/1040672550/az-audit}.

@@

\bibitem[\citeproctext]{ref-herndon2020}
Herndon, Astead W. 2020. {``{LeBron James} and a {Multimillion-Dollar
Push} for {More Poll Workers}.''} \emph{The New York Times: U.S.}
\url{https://www.nytimes.com/2020/08/24/us/politics/lebron-james-poll-workers.html}
(November 13, 2024).

@@

\bibitem[\citeproctext]{ref-kleykamp2023}
Kleykamp, Meredith, Daniel Schwam, and Gilad Wenig. 2023. \emph{What
{Americans Think About Veterans} and {Military Service}: {Findings} from
a {Nationally Representative Survey}}. RAND Corporation.
\url{https://www.rand.org/pubs/research_reports/RRA1363-7.html}.
